Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises

### 2022-07-22 replication_paper/pnas_draft/appendix.Rmd
01-04 reproduce

library(reticulate)
reticulate::py_discover_config()
#use_python("/home/skynet3/anaconda3/bin/python/")
#use_python("/home/tlscherer/anaconda3/bin/python3")

flag_folder_small="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small/"

@@

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft1.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft2.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft3.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft4.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft5.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft6.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft7.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft8.png", zoom=1)

\begin{figure}[H]
\caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft1.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft2.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft3.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft4.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft5.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft6.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft7.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft8.png"}}
\end{figure}

@@

replace_emoticons_cuba <- function(x){
  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q241.png) ") %>%
        #https://emojiterra.com/flag-for-united-states/
        str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
        #https://emojiterra.com/flag-for-russia/
        str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15180.png) ") %>% 
        #Turkey
        str_replace_all('\U0001f1f9\U0001f1f7',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q43.png) ") %>% 
        #U.N.
        str_replace_all('\U0001f1fa\U0001f1f3',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q1065.png) ")
}

@@

ft_cuba_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_cuba_recall.png", zoom=1) # webshot = "webshot2"

\begin{figure}[H]
\caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_cuba_recall.png}}
\end{figure}
\clearpage

@@

replace_emoticons_crimea <- function(x){
      x %>%
            #https://emojiterra.com/flag-for-united-states/
            str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
            #https://emojiterra.com/flag-for-russia/
            str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q159.png) ") %>% 
            #Ukraine
            str_replace_all('\U0001f1fA\U0001f1e6',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q212.png) ") %>% 
            #Crimea
            str_replace_all('Crimea',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15966495.png) ") %>%
            #EU
            str_replace_all('\U0001f1EA\U0001f1FA',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q458.png) ")
}

@@

ft_crimea_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_crimea_recall.png", zoom=1) # webshot = "webshot2"

\begin{figure}[H]
\caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_crimea_recall.png}}
\end{figure}
\clearpage

@@

  ft_crimea_precision_part1 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part1.png", zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part2 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part2.png", zoom=1) # webshot = "webshot2"

@@

\begin{figure}[H]
\caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part1.png}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part2.png}}
\end{figure}
\clearpage

@@

ft_sample_precision_precision1 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision1.png", zoom=1) #

@@

ft_sample_precision_precision2 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision2.png", zoom=1) #

\hphantom{em}
\begin{figure}[H]
\caption{ Stratified Sentence Examples  \label{fig:ft_sample_precision_precision1}}
\centering{\includegraphics[height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision1.png"}}
\end{figure}
\clearpage

\hphantom{em}
\begin{figure}[H]
\centering{\includegraphics[height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision2.png"}}
\end{figure}
\clearpage

@@

  convert_aid = function(x) { x %>% mutate(aid = aid %>% format( scientific = FALSE)) %>% mutate_all(as.character) }
  meta1_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta2_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataBLN-SWB_1979-2019.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataFBIS_1995-2004.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataNYT_1945-2005.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataWSJ_1945-2006.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()

  events_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) # %>% convert_aid() 
  events_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixBLN-SWB_1979-2019.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid() 
  events_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixFBIS_1995-2004.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()  
  events_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixNYT_1945-2005.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()  
  events_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixWSJ_1945-2006.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()

@@

    library(ggtext)
    icews_clean_subset_top10_day <- icews_clean_subset_top10_day %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government|Government","gov")) %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("(tertiary role code)","")) %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross"))
    icews_clean_subset_top10_day %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_lowest.tsv")
    #just out the tsv and plot how you want in the main paper

@@

if(fromscratch){
  p_phoenix_plot_lv0_196 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/p_phoenix_plot_lv0_196.Rds")
  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_196.png'),
            p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_phoenix_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/p_phoenix_plot_lv0_471.Rds")
  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_471.png'),
            p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_terrier_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/p_terrier_plot_lv0_471.Rds")
  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_terrier_plot_lv0_471.png'),
            p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_icews_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/p_icews_plot_lv0_471.Rds")
  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_icews_plot_lv0_471.png'),
            p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

>>>>

library(reticulate)
reticulate::py_discover_config()
#use_python("/home/skynet3/anaconda3/bin/python/")
#reticulate::use_python("/home/tlscherer/anaconda3/bin/python")

flag_folder_small = here::here("replication_data", "in", "flags_small/")

@@

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft1.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft2.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft3.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft4.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft5.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft6.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft7.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft8.png"), zoom=1)

\begin{figure}[H]
\caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft1.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft2.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft3.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft4.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft5.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft6.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft7.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft8.png"}}
\end{figure}

@@

replace_emoticons_cuba <- function(x){
  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")) %>%
        #https://emojiterra.com/flag-for-united-states/
        str_replace_all('\U0001f1fa\U0001f1f8',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
        #https://emojiterra.com/flag-for-russia/
        str_replace_all('\U0001f1f7\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15180.png) ")) %>% 
        #Turkey
        str_replace_all('\U0001f1f9\U0001f1f7',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q43.png) ")) %>% 
        #U.N.
        str_replace_all('\U0001f1fa\U0001f1f3',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q1065.png) "))
}

@@

ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "figures", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"

\begin{figure}[H]
\caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
\centering{\includegraphics[height=21cm]{../figures/ft_cuba_recall.png}}
\end{figure}
\clearpage

@@

replace_emoticons_crimea <- function(x){
      x %>%
            #https://emojiterra.com/flag-for-united-states/
            str_replace_all('\U0001f1fa\U0001f1f8', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
            #https://emojiterra.com/flag-for-russia/
            str_replace_all('\U0001f1f7\U0001f1fa', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q159.png) ")) %>% 
            #Ukraine
            str_replace_all('\U0001f1fA\U0001f1e6', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q212.png) ")) %>% 
            #Crimea
            str_replace_all('Crimea', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15966495.png) ")) %>%
            #EU
            str_replace_all('\U0001f1EA\U0001f1FA', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q458.png) "))
}

@@

ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "figures", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"

\begin{figure}[H]
\caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
\centering{\includegraphics[height=21cm]{../figures/ft_crimea_recall.png}}
\end{figure}
\clearpage

@@

  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "figures", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "figures", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"

@@

\begin{figure}[H]
\caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
\centering{\includegraphics[height=21cm]{../figures/case_study_crimea_precision_part1.png}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[height=21cm]{../figures/case_study_crimea_precision_part2.png}}
\end{figure}
\clearpage

@@

ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "figures", "ft_sample_precision_precision1.png"), zoom=1) #

@@

ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "figures", "ft_sample_precision_precision2.png"), zoom=1) #

\hphantom{em}
\begin{figure}[H]
\caption{ Stratified Sentence Examples  \label{fig:ft_sample_precision_precision1}}
\centering{\includegraphics[height=21cm]{"../figures/ft_sample_precision_precision1.png"}}
\end{figure}
\clearpage

\hphantom{em}
\begin{figure}[H]
\centering{\includegraphics[height=21cm]{"../figures/ft_sample_precision_precision2.png"}}
\end{figure}
\clearpage

@@

  convert_aid = function(x) { x %>% mutate(aid = aid %>% format( scientific = FALSE)) %>% mutate_all(as.character) }
  meta1_nyt2 <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "MetaDataBLN-NYT_1980-2018.csv"), col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta2_swb <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "MetaDataBLN-SWB_1979-2019.csv"), col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_fbis <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "MetaDataFBIS_1995-2004.csv"), col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_nyt <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "MetaDataNYT_1945-2005.csv"), col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_wsj <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "MetaDataWSJ_1945-2006.csv"), col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()

  events_nyt2 <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "PhoenixBLN-NYT_1980-2018.csv"), col_types=rep('c',50)  %>% paste0(collapse='')) # %>% convert_aid() 
  events_swb <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "PhoenixBLN-SWB_1979-2019.csv"), col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid() 
  events_fbis <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "PhoenixFBIS_1995-2004.csv"), col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()  
  events_nyt <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "PhoenixNYT_1945-2005.csv"), col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()  
  events_wsj <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "PhoenixWSJ_1945-2006.csv"), col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()

@@

    library(ggtext)
    icews_clean_subset_top10_day <- icews_clean_subset_top10_day %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government|Government","gov")) %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("(tertiary role code)","")) %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross"))
    icews_clean_subset_top10_day %>% write_tsv(here::here("replication_paper", "data", "out", "icews_clean_471_lowest.tsv"))
    #just out the tsv and plot how you want in the main paper

@@

if(fromscratch){
  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "figures", "p_phoenix_plot_lv0_196.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_196.png'),
            p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "figures", "p_phoenix_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_471.png'),
            p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "figures", "p_terrier_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_terrier_plot_lv0_471.png'),
            p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "figures", "p_icews_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_icews_plot_lv0_471.png'),
            p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```
